Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-08 Documents/Paper/ms.tex
Fixed awkward sentence
cite massinf

\section{Introduction}\label{sec:introduction}
\setlength{\parindent}{0cm}
\setlength{\parskip}{3mm}
Consider the following class of inference problems. There is some unknown
number, $N$, of components in a (physical or metaphorical) region. Each of the $N$ components has parameters
$\xx$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a two-dimensional position and a mass). These problems are often
challenging to solve due to the unknown (and potentially large) dimensionality.
In addition, they also have the so-called ``label-switching degeneracy'' issue
\citep{label_switching}, where the meaning of the model is invariant to
switching the identities of the components. Finite mixture modelling is a common
statistical example.

@@

This is similar to the idea of annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.
Figure~\ref{fig:challenges} shows a mock two dimensional posterior
density with three modes, one of which contains a strong dependence, and
another of which contains a phase transition. The target distribution used by
DNS includes the prior as part of the mixture, so travel between the modes is
possible.

>>>>

\section{Introduction}\label{sec:introduction}
\setlength{\parindent}{0cm}
\setlength{\parskip}{3mm}
Consider the following class of inference problems. There is some unknown
number, $N$, of components in a (physical or metaphorical) region. Each of the $N$ components has parameters
$\xx$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a two-dimensional position and a mass). These problems are often
challenging to solve due to the unknown (and potentially large) dimensionality.
In addition, they also have the so-called ``label-switching degeneracy'' issue
\citep{label_switching}, where the meaning of the model is invariant to
switching the identities of the components. Finite mixture modelling is a common
statistical example, but this kind of problem appears in many other contexts
\citep[e.g.][]{massinf}.

@@

The idea of replacing the target distribution with something other than the
posterior is similar to annealed importance sampling
\citep{neal} or parallel tempering \citep{pt},
where the target distribution is modified from the posterior to something
``easier''. However,
the sequence of distributions used in Nested Sampling avoids some of the
problems with annealing-based methods. In particular, there is no need to choose
a temperature schedule (a potentially large set of tuning parameters),
and the method does not fail when phase transitions
are present.
Figure~\ref{fig:challenges} shows a mock two dimensional posterior
density with three modes, one of which contains a strong dependence, and
another of which contains a phase transition. The target distribution used by
DNS includes the prior as part of the mixture, so travel between the modes is
possible.
